ResearchNotes

### 2014-07-25 ResearchNotes/ResearchNotes.Rmd
Drop forward CV is done.  It works.  Need to write the paper now.

This will be a fairer comparison.  I will boot up each model with 15 observations that then look at how they predict the next day, updating the model each day.

>>>>

This will be a fairer comparison.  I will boot up each model with 20 observations that then look at how they predict the next day, updating the model each day.

OneForwardError<-function(formula, nData){
  model<-lm(formula, data=WTrendsLimited[1:nData,], y=TRUE)
  modelPlus1<-lm(formula, data=WTrendsLimited[1:(nData+1),], y=TRUE)
  predict(model,WTrendsLimited[1+nData,])-tail(modelPlus1$y,1)
}

CVDropForward<-function(model){sd(unlist(lapply(20:(length(WTrendsLimited)-1), FUN= function(x) OneForwardError(model,x))))}

# CVDropForward(HourModel(1))

Lets look at the percent change in drop forward cross validation from the google trends with statistically adjusted model

CompareSigmaCV<-function(x){
SA<-CVDropForward(HourModelForecastCheck(x))  
Google<-CVDropForward(HourModel(x))

CVImprove<-lapply(1:24, FUN = CompareSigmaCV)
CVImprove
mean(unlist(CVImprove))
```
I think the case for 5% is made. The case against their forecasts is very strong anyway.
